\papertitle

### 2017-04-06 paper/paper.tex
First round of corrections done.

%---------------TWO-AUTHOR HEADER STARTS (uncomment below if your paper has two authors)-----------------------
\twoaffiliations{
\paperauthorA \,\sthanks{}}
{\href{http://www.cirmmt.org/}{https://mt.music.mcgill.ca/spcl/home} %
\\ McGill University %
\\ Montreal, Quebec, Canada \\
{\tt \href{mailto:nicholas.esterer@mail.mcgill.ca}{nicholas.esterer@mail.mcgill.ca}}
}
{\paperauthorB \,\sthanks{}}
{\href{http://www.cirmmt.org/}{https://mt.music.mcgill.ca/spcl/home} %
\\ McGill University %
\\ Montreal, Quebec, Canada \\
{\tt %
\href{mailto:philippe.depalle@music.mcgill.ca}{philippe.depalle@music.mcgill.ca}}
}

@@

\section{Introduction}
\label{sec:intro}
Additive synthesis using a sum of sinusoids plus noise is a powerful model for
representing audio \cite{serra1989system}, allowing for the easy implementation
of many manipulations such as time-stretching \cite{marchand2004enhanced} and
timbre-morphing \cite{haken2007beyond}.
%
Here the phase evolution of the sinusoid is assumed linear over
the analysis frame, only the phase and frequency of the sinusoids at these
analysis points are used to fit a plausible phase function after some
the analysis points are connected to form a partial
\cite{mcaulay1986speech}. 
%
Recently, there has
been interest in using higher-order phase functions \cite{xuepiecewise} as the estimation of
their parameters has been made possible by a new set of techniques of only
moderate computational complexity using signal derivatives \cite{hamilton2011non}.
%
The use
of higher-order phase models allows for accurate description of highly modulated
signals, for
example in the analysis of birdsong \cite{stowell2013improved}.
%
The frequency
modulation information has also been used in the
regularization of mathematical programs for audio source separation \cite{creager2016musicalsource}.
%
The sinusoidal model typically considered is
%
\begin{equation}
    \label{eq:polyphaseexp}
    x(t) = \exp(a_0 + \sum_{j=1}^{Q} a_j t^j) + \eta(t)
\end{equation}
where $\eta(t)$ is white gaussian noise.
%
Although this technique can be exteded to describe a single
sinusoid of arbitrary complexity simply by increasing $Q$, it is still of
interest to consider signals featuring a sum of $P$ such components, i.e.,
%
\begin{equation}
    \label{eq:polyphaseexpmix}
    s(t) = \sum_{i=1}^{P} x_{i}(t) + \eta(t)
\end{equation}
%
with
%
\[
    x_{i}(t) = \exp(a_{i,0} + \sum_{j=1}^{Q} a_{i,j} t^j)
\]
%
In situations where multiple signal sources are known to exist (e.g., recordings
of multiple speakers or performers) such a model is plausible.
%
Previous work on these methods has generally assumed signals containing a single
component, i.e., $P=1$ or applied the technique assuming the influence of other
components is negligible. Later we will refine when this assumption can be made.

@@

In this paper, we evaluate the performance of various once-differentiable
windows in estimating the $a_{j}$. We are interested in windows with lower
sidelobes in order to better estimate parameters of sinusoidal chirp signals in
mixture. A technique to design once-differentiable approximations to aribitrary
symmetrical windows is presented along with a design example for a
high-performance window.

%\section{The polynomial phase sinusoid}
%Recently techniques for estimating the parameters of complex polynomial phase sinusoids,
%i.e., signals of the form
%%
%\begin{equation}
%    \label{eq:polyphaseexp}
%    x(t) = \exp(a_0 + \sum_{j=1}^{Q} a_j t^j)
%\end{equation}
%%
%with $a_{j} \in \mathbb{C}$, have been developed. Many techniques
%utilizing derivatives of the signal or the analysis window have
%been developed for estimating the $a_j$. The theoretical equivalence of these
%techniques is described in \cite{hamilton2011non}. This paper focuses on the
%Distribution Derivative Method (DDM) only \cite{betser2009sinusoidal}, as it only requires a once-differentiable
%analysis window and no signal derivatives, which is convenient for signal
%processing applications.
%
%In \cite{hamilton2012comparisons} the accuracy
%of the DDM in estimating each $a_{j}$ is evaluated for $Q=1$ with the constraint
%that $\Re{a_1}=0$ and for $2 \leq Q \leq 3$ with the Hann window used to form
%the test functions. In (Roebel) twice-differentiated windows are used to
%estimate the frequency slopes of chirp signals. Results on the accuracy of
%estimation for signals made of a mixture of chirps are given for the frequency
%slope ($\Im{a_2}$) only, but a variety of windows are compared.
%
%In this paper, we evaluate the performance of various once-differentiable
%windows in estimating the $a_{j}$. We are interested in windows with lower
%sidelobes in order to better estimate parameters of sinusoidal chirp signals in
%mixture. A technique to design once-differentiable approximations to aribitrary
%symmetrical windows is presented along with a design example for a
%high-performance window.

\section{The estimation of $a_j$}
We will now show briefly how the DDM can be used to estimate the $a_j$. Based on
the theory of distributions \cite{schwartz1959theorie}, the DDM
makes use of ``test
functions'' or atoms $\psi$. These atoms must be once differentiable with
respect to time variable $t$ and be non-zero only on a finite interval
$[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$. First, we define
%
\begin{equation}
    \label{eq:ddm:inner:prod:def}
    \left\langle x , \psi \right\rangle = 
    \int_{-\infty}^{\infty}x(t)\overline{\psi}(t)dt
\end{equation}
%
and the operator 
%
\[
\mathcal{T}^{\alpha} : (\mathcal{T}^{\alpha}x)(t) = t^{\alpha}x(t)
\]
%
Consider the weighted signal
%
\[
    f(t) = x(t) \overline{\psi}(t)
\]
%
differentiating with respect to $t$ we obtain
%
\begin{multline}
    \label{eq:ddm:weighted:sig:derivative}
    \frac{df(t)}{dt} = 
    \frac{dx}{dt}(t)\overline{\psi}(t)
    + x(t)\frac{d\overline{\psi}}{dt}(t) \\
    = \left( \sum_{j=1}^{Q} j a_j t^{j-1} \right) x(t)\overline{\psi}(t)
    + x(t)\frac{d\overline{\psi}}{dt}(t)
\end{multline}
%
Because $\psi$ is zero outside of the interval $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$, integrating
$\frac{df(t)}{dt}$ we obtain
%
\begin{multline*}
    \int_{-\infty}^{\infty}\frac{df(t)}{dt}dt \\
    = \sum_{j=1}^{Q} j a_j \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} t^{j-1} x(t) \overline{\psi}(t) dt
    + \left\langle x, \frac{d\overline{\psi}}{dt} \right\rangle = 0
\end{multline*}
%
or, using the operator $\mathcal{T}^{\alpha}$,
%
\[ 
    \sum_{j=1}^{Q} j a_j 
    \left\langle \mathcal{T}^{j-1} x , \overline{\psi} \right\rangle
    = -\left\langle x, \frac{d\overline{\psi}}{dt} \right\rangle
\]
%

From this we can see that to estimate the coefficients $a_j$, $ 1 \leq q \leq Q
$ we simply need $R$ atoms with $R \geq Q$ to solve the linear system of
equations
\begin{equation}
    \label{eq:ddmsyseq}
    \sum_{j=1}^{Q} j a_j 
    \left\langle \mathcal{T}^{j-1} x , \overline{\psi}_{r} \right\rangle
    = -\left\langle x, \frac{d\overline{\psi}_{r}}{dt} \right\rangle
\end{equation}
for $1 \leq r \leq R$.

To estimate $a_0$ we write the signal we are analysing as
\[
    x(t) = \exp(a_0) \gamma(t) + \epsilon (t)
\]
where $\epsilon (t)$ is the error signal, the part of the signal that is not explained
by our model, and $\gamma (t)$ is the part of the signal
whose coefficients have already been estimated, i.e.,
\[
    \gamma(t) = \exp \left( \sum_{j=1}^{Q} a_j t^{j} \right)
\]
Computing the inner product $\left\langle x , \gamma \right\rangle$, we have
\[
    \left\langle x , \gamma \right\rangle
    =
    \left\langle \exp(a_0) \gamma , \gamma \right\rangle + 
        \left\langle \epsilon , \gamma \right\rangle
\]
The inner-product between $\epsilon$ and $\gamma$ is $0$, by the orthogonality
principle \cite[ch.~12]{kay1993fundamentals}. Furthermore, because $\exp(a_0)$ does not
depend on $t$, we have
\[
    \left\langle x , \gamma \right\rangle
    =
    \exp(a_0) \left\langle \gamma , \gamma \right\rangle
\]
so we can estimate $a_0$ as
\begin{equation}
    \label{eq:ddmesta0}
    a_0 = \log \left( \left\langle x , \gamma \right\rangle \right)
        - \log \left( \left\langle \gamma , \gamma \right\rangle \right)
\end{equation}

\section{The estimation of the $a_{i,j}$ of $P$ components}

We examine how the mixture model influences the estimation of the $a_{i,j}$ in
Eq.~\ref{eq:polyphaseexpmix}.
Consider a mixture of $P$ components.
If we define the weighted signal sum
%
\[
    g(t) = \sum_{i=1}^{P} x_{i}(t) \overline{\psi}(t) = \sum_{i=1}^{P} f_{i}(t)
\]
%
and substitute $g$ for $f$ in Eq.~\ref{eq:ddm:weighted:sig:derivative} we obtain
%
\begin{multline}
    \label{eq:mixest}
    \sum_{i=1}^{P} \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} \frac{df_{i}}{dt}(t) =
    0
    \\ = 
    \sum_{i=1}^{P}
    \sum_{j=1}^{Q} j a_{i,j} 
    \left\langle \mathcal{T}^{j-1} x_i , \overline{\psi} \right\rangle
     + \left\langle x_i, \frac{d\overline{\psi}}{dt} \right\rangle
\end{multline}
%
From this we see if $\left\langle \mathcal{T}^{j-1} x_i , \overline{\psi}_{r}
\right\rangle$ and $\left\langle x_i, \frac{d\overline{\psi_{r}}}{dt} \right\rangle$
are small for all but $i = i^{\ast}$ and a subset of $R$ atoms, we
can simply estimate the parameters $a_{i^{\ast},j}$ using
\[
    \sum_{j=1}^{Q} j a_{{i^{\ast}},j} 
    \left\langle \mathcal{T}^{j-1} x_{i^{\ast}} , \overline{\psi}_{r} \right\rangle
    = -\left\langle x_{i^{\ast}}, \frac{d\overline{\psi}_{r}}{dn} \right\rangle
\]
for $1 \leq r \leq R$. To compute $a_{i^{\ast},0}$ we simply use
\[
    \gamma_{i^{\ast}}(t) = \exp \left( \sum_{j=1}^{Q} a_{i^{\ast},j} t^{j} \right)
\]
in place of $\gamma$ in Eq.~\ref{eq:ddmesta0}.

\section{Designing the $\psi_{r}$}
\label{sec:designingatoms}
%
\begin{figure*}[t]
    \centerline{\includegraphics[width=7in]{{search_dpw_bw_m}.eps}}
\caption{\label{fig:dpw} Comparing the main-lobe and asymptotic power
spectrum characteristics of the continuous 4-term Nuttall window, the digital
prolate window with $W=0.008$, and the continuous approximation to the digital
prolate window.}
\end{figure*}
%
In practice, an approximation of Eq.~\ref{eq:ddm:inner:prod:def} is evaluated using
the discrete Fourier transform (DFT) on a signal $x$ that is properly sampled
and so can be evaluated at a finite number of points $nT$ with $n \in [0,N-1]$ and
$T$ the sample period in seconds. In this way, the atoms $\psi_{\omega}(t)$ chosen
are the products of the elements of the Fourier basis and an appropriately
chosen window $w$ that is once differentiable and finite, i.e.,
%
\[
    \psi_{\omega}(t) = w(t) \exp(-\sqrt{-1} \omega t)
\]
%
Defining $N = \frac{L_{t}}{T}$ and $\omega = 2
\pi \frac{r}{N}$, the approximate
inner product is then
%
\[
    \left\langle x , \psi_{\omega} \right\rangle \approx 
    \sum_{n=0}^{N-1} x(Tn) w(Tn) \exp(-2 \pi \sqrt{-1} r \frac{n}{N}) 
\]
%
i.e., the definition of the DFT of a windowed signal.%
\footnote{%
    Notice however that this is an approximation of the inner product and should
    not be interpreted as yielding the Fourier series coefficients of a properly
    sampled signal $x$ periodic in $L_{t}$. This means that other
    evaluations of the inner product that yield more accurate results are
    possible. For example, the analytic solution is possible if $x$ is assumed
    zero outside of $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$ (the $\psi$ are in
    general analytic).  In this case the samples of $x$ are convolved with the
    appropriate interpolating sinc functions and the integral of this function's
    product with $\psi$ is evaluated.
}%
The DFT is readily interpreted as a bank of bandpass filters centred at
normalized frequencies%
\footnote{%
In this article as in much of the literature on signal processing the index $r$
of the Fourier basis element corresponding to the frequency $\omega_{r} = 2 \pi
\frac{r}{N}$ will be referred to as its bin number.
}
$\frac{r}{N}$ and with frequency response described by the Fourier transform of
modulated $w$ \cite{allen1977unified}. Therefore choosing $\psi$ amounts to a
filter design problem under the constraints that the impulse response of the
filter be differentiable in $t$ and finite. To minimize the influence of all but
one component, granted the components's energy concentrations are sufficiently
separated in frequency, we desire impulse responses whose magnitude response
gives maximum out-of-band rejection or equivalently, windows whose Fourier
transform exhibits the lowest sidelobes.

In all the publications these authors reviewed on the DDM, the window used was
the Hann window which is once-differentiable everywhere in the time-domain. In
\cite{robel2002estimating}, a publication on the reassignment method, other
windows than the Hann are considered but these windows must be
twice-differentiable.  Nuttall \cite{nuttall1981some} has designed windows with
lower sidelobes than the canonical Hann window which are everywhere at least
once-differentiable. It is also possible to design approximations to aribtrary
symmetrical window functions using harmonically related cosines, as is discussed
in the following section.

\section{Differentiable approximations to windows}
%
\begin{figure*}[ht]
    \centerline{\includegraphics[width=7in]{{ddm_snr_win_comp}.eps}}
\caption{\label{fig:snrwincomp} The estimation variance of random polynomial
    phase sinusoids averaged over $K_{1}=\Ksnr{}$ trials using atoms generated from
    various windows. \textit{C} is the Cram\'{e}r-Rao
lower bound, \textit{N3} and \textit{N4} are the 3- and 4-cosine-term continuous
Nuttall windows, \textit{H} is the Hann window, and \textit{P5} is the continous
5-cosine-term approximation to a digital prolate window as described in
Sec.~\ref{sec:designexample}.}
\end{figure*}
%
A differentiable approximation to a symmetrical window can be designed in a
straightforward way. In \cite{harris1978use} and \cite{rabiner1970approach} it
is shown how to design optimal windows of length $N$ samples using a linear
combination of $M$ harmonically related cosines
\begin{equation}
    w(n) = \sum_{k=0}^{M-1} b_{k} \cos (2 \pi k \frac{n}{N})
\mathcal{R}(\frac{n}{N})
\end{equation}
where $\mathcal{R}$ is the \textit{rectangle function}. This function is
discontinuous
at $n = \frac{\pm N}{2}$, and therefore not differentiable there, unless
\[
\sum_{k=0}^{M-1} b_{k} \cos ( \pm \pi k ) = 0
\]

@@

\section{A continuous window design example}
\label{sec:designexample}
%
\begin{figure*}[ht]
    \centerline{\includegraphics[width=7in]{{comp_offset_chirp_est_err_params}.eps}}
\caption{\label{fig:mixwincomp} The mean squared estimation error for each
    parameter in an analysis of two components in mixture. A set of
    $K_{2}=\Koffset{}$ chirps was synthesized and each unique pair used for
    maximum bin differences $0 \leq d < \Doffset{}$. The signal power ratio
    between components is indicated using shades of grey: lighter shades
    indicate a ratio closer to $1$. The ratio in decibels is indicated in the
    plot legend. The names indicate the windows used to generate the atoms for
    estimation: \textit{N3} and \textit{N4} are the 3- and 4-cosine-term
    continuous Nuttall windows, \textit{H} is the Hann window, and \textit{P5}
is the continous 5-cosine-term approximation to a digital prolate window as
described in Sec.~\ref{sec:designexample}.}
\end{figure*}
%
As a design example we show how to create a continuous approximation of a digital
prolate spheroidal window.

@@

In \cite{verma1996digital} it was shown how to construct digital prolate
spheroidal windows under parameters $N$, the window length in samples, and a
parameter $W$. We chose $N=512$ based on the window length chosen in
\cite{betser2009sinusoidal} for ease of comparison. Its $W$ parameter's value
was chosen by synthesizing windows with $W$ ranging between $0.005$ and $0.010$
at a resolution of $0.001$. The window with the closest 3db bandwidth to the
4-term Nuttall window was obtained with $W=0.008$. Its magnitude response is
shown in Fig.~\ref{fig:dpw}. We see that
this window's asymptotic falloff is 6 dB per octave and therefore has a
discontinuity somewhere in its domain \cite{nuttall1981some}. We designed an approximate
window using Eq.~\ref{eq:searchcontwinprogram} for $M$ varying between $2$ and
$N/8$ to find the best approximation to the digital prolate window's main lobe
using a small number of cosines. The $M$ giving the best approximation was $5$.
The magnitude response of the approximation is shown in
Fig.~\ref{fig:dpw}.  We see that we obtain a lower highest sidelobe
level than the Nuttall and Prolate windows by slightly sarificing the narrowness
of the main lobe. Furthermore in Fig.~\ref{fig:dpw} we observe that
the falloff of the window is 18 dB per octave because it is once-differentiable
at all points in its domain.

>>>>

%---------------TWO-AUTHOR HEADER STARTS (uncomment below if your paper has two authors)-----------------------
\twoaffiliations{
\paperauthorA \,}
{\href{http://www.cirmmt.org/}{%Sound Processing and Control Laboratory
        SPCL %
        \sthanks{Sound Processing and Control Laboratory} \\%
%        Centre for Interdisciplinary Research in Music Media and Technology
        CIRMMT %
        \sthanks{Centre for Interdisciplinary Research in Music Media and Technology}%
    }
\\ McGill University %
\\ Montreal, Quebec, Canada \\
{\tt \href{mailto:nicholas.esterer@mail.mcgill.ca}{nicholas.esterer@mail.mcgill.ca}}
}
{\paperauthorB \,}
{\href{http://www.cirmmt.org/}{%Sound Processing and Control Laboratory
        SPCL \\%
%        \sthanks{Sound Processing and Control Laboratory} \\%
%        Centre for Interdisciplinary Research in Music Media and Technology
        CIRMMT %
%        \sthanks{Centre for Interdisciplinary Research in Music Media and Technology}%
    } %
\\ McGill University %
\\ Montreal, Quebec, Canada \\
{\tt %
\href{mailto:philippe.depalle@mcgill.ca}{philippe.depalle@mcgill.ca}}
}

@@

\section{Introduction}
\label{sec:intro}
Additive synthesis using a sum of sinusoids plus noise is a powerful model for
representing audio \cite{serra1989system}, allowing for the easy implementation
of many manipulations such as time-stretching \cite{marchand2004enhanced} and
timbre-morphing \cite{haken2007beyond}.
%
Here the phase evolution of the sinusoid is assumed linear over
the analysis frame, only the phase and frequency of the sinusoids at these
analysis points are used to fit a plausible phase function after some
the analysis points are connected to form a partial
\cite{mcaulay1986speech}. 
%
Recently, there has
been interest in using higher-order phase functions \cite{xuepiecewise} as the estimation of
their parameters has been made possible by a new set of techniques of only
moderate computational complexity using signal derivatives \cite{hamilton2012unified}.
%
The use
of higher-order phase models allows for accurate description of highly modulated
signals, for
example in the analysis of birdsong \cite{stowell2013improved}.
%
The frequency
modulation information has also been used in the
regularization of mathematical programs for audio source separation \cite{creager2016musicalsource}.
%
The sinusoidal model typically considered is
%
\begin{equation}
    \label{eq:polyphaseexp}
    s(t) = \exp(a_0 + \sum_{j=1}^{Q} a_j t^j) + \eta(t)
\end{equation}
where $\eta(t)$ is white Gaussian noise.
%
Although this technique can be extended to describe a single
sinusoid of arbitrary complexity simply by increasing $Q$, it is still of
interest to consider signals featuring a sum of $P$ such components, i.e.,
%
\begin{equation}
    \label{eq:polyphaseexpmix}
    x(t) = \sum_{i=1}^{P} x_{i}(t) + \eta(t)
\end{equation}
%
with
%
\[
    x_{i}(t) = \exp(a_{i,0} + \sum_{j=1}^{Q} a_{i,j} t^j)
\]
%
In situations where multiple signal sources are known to exist (e.g., recordings
of multiple speakers or performers) such a model is plausible.
%
Previous work on these methods has generally assumed signals containing a single
component, i.e., $P=1$ or applied the technique assuming the influence of other
components is negligible. Later we will refine when this assumption can be made.

@@

In this paper, we evaluate the performance of various once-differentiable
windows in estimating the coefficients
$a_{j}$. We are interested in windows with lower sidelobes in order to better
estimate parameters of sinusoidal chirp signals in mixture. A technique to
design once-differentiable approximations to arbitrary symmetrical windows is
presented along with a design example for a high-performance window.

\section{Estimating the \lowercase{$a_{j}$}}
We will now show briefly how the DDM can be used to estimate the $a_j$. Based on
the theory of distributions \cite{schwartz1959theorie}, the DDM
makes use of ``test
functions'' or atoms $\psi$. These atoms must be once differentiable with
respect to time variable $t$ and be non-zero only on a finite interval
$[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$. First, we define
%
\begin{equation}
    \label{eq:ddm:inner:prod:def}
    \left\langle x , \psi \right\rangle = 
    \int_{-\infty}^{\infty}x(t)\overline{\psi}(t)dt
\end{equation}
%
and the operator 
%
\[
\mathcal{T}^{\alpha} : (\mathcal{T}^{\alpha}x)(t) = t^{\alpha}x(t)
\]
%
Consider the weighted signal
%
\[
    f(t) = x(t) \overline{\psi}(t)
\]
%
differentiating with respect to $t$ we obtain
%
\begin{multline}
    \label{eq:ddm:weighted:sig:derivative}
    \frac{df(t)}{dt} = 
    \frac{dx}{dt}(t)\overline{\psi}(t)
    + x(t)\frac{d\overline{\psi}}{dt}(t) = \\
    \left( \sum_{j=1}^{Q} j a_j t^{j-1} \right) x(t)\overline{\psi}(t)
    + x(t)\frac{d\overline{\psi}}{dt}(t)
\end{multline}
%
Because $\psi$ is zero outside of the interval $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$, integrating
$\frac{df(t)}{dt}dt$ we obtain
%
\begin{multline*}
    \int_{-\infty}^{\infty}\frac{df(t)}{dt}dt = \\
    \sum_{j=1}^{Q} j a_j \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} t^{j-1} x(t) \overline{\psi}(t) dt
    + \left\langle x, \frac{d\overline{\psi}}{dt} \right\rangle = 0
\end{multline*}
%
or, using the operator $\mathcal{T}^{\alpha}$,
%
\[ 
    \sum_{j=1}^{Q} j a_j 
    \left\langle \mathcal{T}^{j-1} x , \overline{\psi} \right\rangle
    = -\left\langle x, \frac{d\overline{\psi}}{dt} \right\rangle
\]
%

Estimating coefficients $a_j$, ${1 < j \leq Q}$,
simply requires $R$ atoms with $R \geq Q$ to solve the linear system of
equations
\begin{equation}
    \label{eq:ddmsyseq}
    \sum_{j=1}^{Q} j a_j 
    \left\langle \mathcal{T}^{j-1} x , \overline{\psi}_{r} \right\rangle
    = -\left\langle x, \frac{d\overline{\psi}_{r}}{dt} \right\rangle
\end{equation}
for $1 \leq r \leq R$.

To estimate $a_0$ we rewrite the signal we are analysing as
\[
    x(t) = \exp(a_0) \gamma(t) + \epsilon (t)
\]
where $\epsilon (t)$ is the error signal, the part of the signal that is not explained
by our model, and $\gamma (t)$ is the part of the signal
whose coefficients have already been estimated, i.e.,
\[
    \gamma(t) = \exp \left( \sum_{j=1}^{Q} a_j t^{j} \right)
\]
Computing the inner product $\left\langle x , \gamma \right\rangle$, we have
\[
    \left\langle x , \gamma \right\rangle
    =
    \left\langle \exp(a_0) \gamma , \gamma \right\rangle + 
        \left\langle \epsilon , \gamma \right\rangle
\]
The inner product between $\epsilon$ and $\gamma$ is $0$, by the orthogonality
principle \cite[ch.~12]{kay1993fundamentals}. Furthermore, because $\exp(a_0)$ does not
depend on $t$, we have
\[
    \left\langle x , \gamma \right\rangle
    =
    \exp(a_0) \left\langle \gamma , \gamma \right\rangle
\]
so we can estimate $a_0$ as
\begin{equation}
    \label{eq:ddmesta0}
    a_0 = \log \left( \left\langle x , \gamma \right\rangle \right)
        - \log \left( \left\langle \gamma , \gamma \right\rangle \right)
\end{equation}

\section{Estimating the \lowercase{$a_{i,j}$} of $P$ components}

We examine how the mixture model influences the estimation of the $a_{i,j}$ in
Eq.~\ref{eq:polyphaseexpmix}.
Consider a mixture of $P$ components.
If we define the weighted signal sum
%
\[
    g(t) = \sum_{i=1}^{P} x_{i}(t) \overline{\psi}(t) = \sum_{i=1}^{P} f_{i}(t)
\]
%
and substitute $g$ for $f$ in Eq.~\ref{eq:ddm:weighted:sig:derivative} we obtain
%
\begin{multline}
    \label{eq:mixest}
    \sum_{i=1}^{P} \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}}
    \frac{df_{i}}{dt}(t)dt =
    0
    \\ = 
    \sum_{i=1}^{P} \left(
    \sum_{j=1}^{Q} j a_{i,j} 
    \left\langle \mathcal{T}^{j-1} x_i , \overline{\psi} \right\rangle
    + \left\langle x_i, \frac{d\overline{\psi}}{dt} \right\rangle \right)
\end{multline}
%
From this we see if $\left\langle \mathcal{T}^{j-1} x_i , \overline{\psi}_{r}
\right\rangle$ and $\left\langle x_i, \frac{d\overline{\psi_{r}}}{dt} \right\rangle$
are small for all but $i = i^{\ast}$ and a subset of $R$ atoms, we
can simply estimate the parameters $a_{i^{\ast},j}$ using
\[
    \sum_{j=1}^{Q} j a_{{i^{\ast}},j} 
    \left\langle \mathcal{T}^{j-1} x_{i^{\ast}} , \overline{\psi}_{r} \right\rangle
    = -\left\langle x_{i^{\ast}}, \frac{d\overline{\psi}_{r}}{dn} \right\rangle
\]
for $1 \leq r \leq R$. To compute $a_{i^{\ast},0}$ we simply use
\[
    \gamma_{i^{\ast}}(t) = \exp \left( \sum_{j=1}^{Q} a_{i^{\ast},j} t^{j} \right)
\]
in place of $\gamma$ in Eq.~\ref{eq:ddmesta0}.

\section{Designing the $\psi_{r}$}
\label{sec:designingatoms}
%
\begin{figure*}[t]
    \centerline{\includegraphics[width=7in]{{search_dpw_bw_m}.eps}}
\caption{\label{fig:dpw} Comparing the main-lobe and asymptotic power
spectrum characteristics of the continuous 4-term Nuttall window, the digital
prolate window with $W=0.008$, and the continuous approximation to the digital
prolate window.}
\end{figure*}
%
In practice, an approximation of Eq.~\ref{eq:ddm:inner:prod:def} is evaluated using
the discrete Fourier transform (DFT) on a signal $x$ that is properly sampled
and so can be evaluated at a finite number of points $nT$ with $n \in [0,N-1]$ and
$T$ the sample period in seconds. In this way, the chosen atoms $\psi_{\omega}(t)$ 
are the products of the elements of the Fourier basis and an appropriately
chosen window $w$ that is once differentiable and finite, i.e.,
%
\[
    \psi_{\omega}(t) = w(t) \exp(-\sqrt{-1} \omega t)
\]
%
Defining $N = \frac{L_{t}}{T}$ and $\omega = 2
\pi \frac{r}{N}$, the approximate
inner product is then
%
\[
    \left\langle x , \psi_{\omega} \right\rangle \approx 
    \sum_{n=0}^{N-1} x(Tn) w(Tn) \exp(-2 \pi \sqrt{-1} r \frac{n}{N}) 
\]
%
i.e., the definition of the DFT of a windowed signal.%
\footnote{%
    Notice however that this is an approximation of the inner product and should
    not be interpreted as yielding the Fourier series coefficients of a properly
    sampled signal $x$ periodic in $L_{t}$. This means that other
    evaluations of the inner product that yield more accurate results are
    possible. For example, the analytic solution is possible if $x$ is assumed
    zero outside of $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$ (the $\psi$ are in
    general analytic).  In this case the samples of $x$ are convolved with the
    appropriate interpolating sinc functions and the integral of this function's
    product with $\psi$ is evaluated.
}%
The DFT is readily interpreted as a bank of bandpass filters centred at
normalized frequencies%
\footnote{%
In this article as in much of the literature on signal processing the index $r$
of the Fourier basis element corresponding to the frequency $\omega_{r} = 2 \pi
\frac{r}{N}$ will be referred to as its bin number.
}
$\frac{r}{N}$ and with frequency response described by the Fourier transform of
modulated $w$ \cite{allen1977unified}. Therefore choosing $\psi$ amounts to a
filter design problem under the constraints that the impulse response of the
filter be differentiable in $t$ and finite. To minimize the influence of all but
one component, granted the components's energy concentrations are sufficiently
separated in frequency, we desire impulse responses whose magnitude response
gives maximum out-of-band rejection or equivalently, windows whose Fourier
transform exhibits the lowest sidelobes.

In all the publications reviewed on the DDM for this paper, the window used was
the Hann window which is once-differentiable everywhere in the time-domain. In
\cite{robel2002estimating}, a publication on the reassignment method, other
windows than the Hann are considered but these windows must be
twice-differentiable.  Nuttall \cite{nuttall1981some} has designed windows with
lower sidelobes than the canonical Hann window which are everywhere at least
once-differentiable. It is also possible to design approximations to arbitrary
symmetrical window functions using harmonically related cosines, as is discussed
in the following section.

\section{Differentiable approximations to windows}
%
\begin{figure*}[ht]
    \centerline{\includegraphics[width=7in]{{ddm_snr_win_comp}.eps}}
\caption{\label{fig:snrwincomp} The estimation variance of random polynomial
    phase sinusoids averaged over $K_{1}=\Ksnr{}$ trials using atoms generated from
    various windows. \textit{C} is the Cram\'{e}r-Rao
lower bound, \textit{N3} and \textit{N4} are the 3- and 4-cosine-term continuous
Nuttall windows, \textit{H} is the Hann window, and \textit{P5} is the continuous
5-cosine-term approximation to a digital prolate window as described in
Sec.~\ref{sec:designexample}.}
\end{figure*}
%
A differentiable approximation to a symmetrical window can be designed in a
straightforward way. In \cite{harris1978use} and \cite{rabiner1970approach} it
is shown how to design optimal windows of length $N$ samples using a linear
combination of $M$ harmonically related cosines
\begin{equation}
    w(n) = \sum_{k=0}^{M-1} b_{k} \cos (2 \pi k \frac{n}{N})
\mathcal{R}(\frac{n}{N})
\end{equation}
where $\mathcal{R}$ is the \textit{rectangle function}. This function is
discontinuous
at $n = \frac{\pm N}{2}$, and therefore not differentiable there, unless
\[
\sum_{k=0}^{M-1} b_{k} \cos ( \pm \pi k ) = 0
\]

@@

\section{A continuous window design example}
\label{sec:designexample}
%
\begin{figure*}[ht]
    \centerline{\includegraphics[width=7in]{{comp_offset_chirp_est_err_params}.eps}}
\caption{\label{fig:mixwincomp} The mean squared estimation error for each
    parameter in an analysis of two components in mixture. A set of
    $K_{2}=\Koffset{}$ chirps was synthesized and each unique pair used for
    maximum bin differences $0 \leq d < \Doffset{}$. The signal power ratio
    between components is indicated using shades of grey: lighter shades
    indicate a ratio closer to $1$. The ratio in decibels is indicated in the
    plot legend. The names indicate the windows used to generate the atoms for
    estimation: \textit{N3} and \textit{N4} are the 3- and 4-cosine-term
    continuous Nuttall windows, \textit{H} is the Hann window, and \textit{P5}
is the continuous 5-cosine-term approximation to a digital prolate window as
described in Sec.~\ref{sec:designexample}.}
\end{figure*}
%
As a design example we show how to create a continuous approximation of a digital
prolate spheroidal window.

@@

In \cite{verma1996digital} it was shown how to construct digital prolate
spheroidal windows under parameters $N$, the window length in samples, and a
parameter $W$ choosing the (normalized) frequency range in which the proportion
of the main lobe's energy is to be maximized. We chose $N=512$ based on the
window length chosen in \cite{betser2009sinusoidal} for ease of comparison. Its
$W$ parameter's value was chosen by synthesizing windows with $W$ ranging
between $0.005$ and $0.010$ at a resolution of $0.001$. The window with the
closest 3 dB bandwidth to the 4-term Nuttall window was obtained with $W=0.008$.
Its magnitude response is shown in Fig.~\ref{fig:dpw}. We see that this window's
asymptotic falloff is 6 dB per octave and therefore has a discontinuity
somewhere in its domain \cite{nuttall1981some}. We designed an approximate
window using Eq.~\ref{eq:searchcontwinprogram} for $M$ varying between $2$ and
$N/8$ to find the best approximation to the digital prolate window's main lobe
using a small number of cosines. The $M$ giving the best approximation was $5$.
The magnitude response of the approximation is shown in Fig.~\ref{fig:dpw}.  We
see that we obtain a lower highest sidelobe level than the Nuttall and Prolate
windows by slightly sacrificing the narrowness of the main lobe. Furthermore in
Fig.~\ref{fig:dpw} we observe that the falloff of the window is 18 dB per octave
because it is once-differentiable at all points in its domain.
